Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2015-05-30 unstructured.tex
2015.05.30 (Vassilis) Changes added based on Hüseyin's comments. Mainly minor re-wording and fixing typos.

The \emph{directed BFS}
tries to avoid the aforementioned delay by forwarding 
query messages only to a selected subset of available neighbors. The selection
criteria varies, from the number of results received or the distance (hops)
traveled to locate these results, to the bandwidth, or the
query load of the neighbor. That way, fewer nodes are visited but quality of
query responses is maintained, to a large degree, on the premise that the
selected heuristics can direct the search to the right path.
%
In \emph{local indices},
each node indexes data hosted by neighboring nodes within a radius of $r$ hops
and uses this local index to answer queries on behalf of other nodes.
That way, local indices,
greatly reduce the aggregate bandwidth usage of the network and 
improve query efficiency. However, updating such indices in 
the presence of frequent node joins/departures 
may introduce significant overhead should the radius is kept broad.
%%
Below, we outline how the techniques in~\cite{YG-M2002}
fare against the $3$ major performance criteria 
of Section~\ref{section:background}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \paragraph*{ \bf Delay Aware P2P System}
A \emph{delay--aware} \p\ system termed {\sl DAPS} 
was introduced in~\cite{ZL2005}.
{\sl DAPS}  seeks to attain reduced look-up times by dividing 
peer routing tables into several sectors of increasing delay. 
The source node that issues the query designates the delay 
boundary it may tolerate, providing so a \emph{pruning factor}.
In this context, user requests are forwarded only to 
nodes whose expected delay is less than or equal to the indicated boundary. 
{\sl DAPS} primarily focuses on user ``experience'' and deploys an
end-to-end delay monitoring mechanism that may enable
the clustering of routing tables. 
In an dynamic environment, the formation 
of very accurate such routing tables might be however an elusive goal.
%With the clustered
%routing tables and the loose organization of DAPS' overlay network it is
%considered by is be tween structured and unstructured.
%%
In terms of the $3$ performance criteria, {\sl DAPS} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Does not check for close by nodes, it just sorts the contents of a node's
% routing table.
% Also in a high churn environment a lot of time could be spend probing for
% distances, resorting routing tables and creating sectors. Moreover it just
% prunes distant neighbor
low &
% Sorting routing table entries is done locally so it is not affecting.
low &
%
medium
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Gia}
The key objective of the {\sl Gia} system~\cite{CRBLS2003} is 
to help alleviate the scalability omnipresent
in unstructured \p\ file-sharing systems.
At first, {\sl Gia} replaced {\sl Gnutella}'s blind flooding 
with random walks.
Although this adoption was 
a step in the right direction \cite{LCCLS2002},
issuing a single copy of the query within the network
effectively reduces the search scope and may negatively affect 
the success rate of the query in question.
To overcome this limitation, {\sl Gia} introduces
a token-based flow control mechanism 
that gradually redirects queries to nodes which are more
likely to answer. This flow control mechanism also helps prevent node
overloading as each peer ``announces'' the number of query requests it 
can handle, in terms of tokens, to its neighbors; to this end, 
peers only forward query requests to nodes that they previously
received tokens from. Further refinement to the search mechanism is the
support for \emph{one--hop replication} of pointers to content.
{\sl Gia} also acknowledges the heterogeneity in peer bandwidth,
processing power, disk speed, etc., of \p\ nodes and uses this
information when connecting nodes to each other.
By using a topology adaptation algorithm, 
{\sl Gia} places low capacity nodes within 
short proximity to peers with high performance features.
This topology adaptation algorithm is based on the metric 
each node maintains about its satisfaction --ranging between $0$ and $1$--
for the neighbors it finds itself associated with. 
Through message exchange, a peer can establish new connections 
or drop superseded ones in order to improve its satisfaction.
Despite the fact that {\sl Gia}'s topology adaptation algorithm 
that primarily focuses on the satisfaction of peers improves the network's 
scalability it falls short in addressing the mismatch problem
as considerations for the underlying network are not handled in explicit
terms \cite{LXLNZ2005}. Moreover it reduces the search scope, exhibits poor
performance in the worst case when matching data is not found quickly
\cite{PR2004,HJ2004} and can potentially build  disconnected topologies
\cite{MBL2006}.
%
In terms of the $3$ stated criteria, {\sl Gia}'s approach is as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Reduces the search scope.
medium &
% Only one copy of the query is issued to the network.
% A token based flow control mechanism redirects queries to nodes that are most
% likely to fulfill them.
low &
% Even thought the low overhead scalability is reduced by the reducing of
% search scope.
medium
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Distributed Cycle Minimization Protocol (DCMP)}
Another problem with topology unaware
systems is the duplication of messages due to cycles in the network graph.
Interestingly, such cycles appear even along the correct forwarding path.
\cite{ZKB2008} focuses on this exact deficiency of overlay networks and
introduces the \emph{Distributed Cycle Minimization Protocol
(DCMP)}, a dynamic, fully distributed method that removes cycles;
this is accomplished without sacrificing
overlay connectivity, resilience and other key properties of unstructured
\p\ architectures and by avoiding a hierarchical organization of peers. 
Once a cycle is detected in {\it DCMP}, the most powerful node in that cycle 
is elected as the \emph{Gate Peer} and the cycle is then broken in that place
that it will result in the minimization of the distance between the
\emph{Gate Peer} and all other nodes that are currently part of the cycle. 
This process is managed by using two specialized message types 
namely, \emph{Information Collection Message (ICM)} and \emph{Cut Message (CM)}. 
\emph{DCMP} bases its operation on messages whose travel is limited by an
imposed \emph{TTL} value (max set to $7$ for most cases). This inherently limits
the protocol in detecting cycles that span for more than \emph{TTL} nodes.
Even though cycle elimination does improve network performance, 
it cannot  directly contribute to the solution of the topology mismatch
problem, while its performance in a high traffic and churn environments and its
ability to retain important characteristics of a {\sl Gnutella}-like topology (i.e.,
like degree distribution, average peer distance, diameter e.t.c.) has been
doubted~\cite{CSG2010}. 
On the other hand, even though some of the overhead
saved by the duplicate message reduction is spent to control the cycle cutting
mechanism it is reported that still stays for example one to two orders of
magnitude less than LTM due to its ``lazy'' broadcasting of control messages
(as opposed to LTM's periodic approach) \cite{ZKB2008}.
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/dcmp.jpeg}
%\caption{Cycle elimination methods in DCMP}
%\label{figure:dcmp}
%\end{figure}
%
% TODO: SOME DISCUSSION
%Actually, the duplicate packet problem seems to hurt more the active nodes;
%those with higher capacities and bandwidth that contribute the most to the
%network.
The expected \emph{DCMP} behavior as far as our $3$ criteria is:
%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It returns more result than LTM according to experiments in
% \cite{ZKB2008}
medium &
% Duplicates are an important fraction of the redundant overhead imposed by
% topology mismatch and thus DCMP minimizes this as possible.
low &
% fully distributed method
high
\end{tabular}
}
\end{center}

In \cite{CS2002} and \cite{LCCLS2002}, replication is used as a way to improve
inefficient blind search. The observation is that as the number of replicas
increases in the network, it would be relatively easy to locate items even if
search is random.

The work discusses $3$ approaches for replication allocation namely \emph{uniform},
\emph{proportional}, and \emph{square-root replication}. In the uniform model,
all objects are replicated without taking into account the query distribution,
while in the proportional, objects are replicated analogously to their query
rate, so that frequently queried items can be found more often. Experimental
outcomes indicate that the uniform allocation minimizes the maximum search
length and so it can reduce the time spent on unsuccessful searches. The
proportional strategy effectively decreases the search time for popular items,
but suffers when needing to locate the rare entities. When it comes to expected
successful search size, it is the same for for both uniform and proportional
models and any approach in between to always behave much better. Finally, the
square-root model is an attempt to find the golden ratio between uniform and
proportional allocation models. It suggests setting the number of object
replicas to the square root of the searching rate for an object\footnote{An
interesting application of the square-root principle has also been explored
in the context of topology reconstruction, by ensuring node degree to be
proportional to the square-root of its content popularity \cite{C2005}.}.
Theory in \cite{CS2002} suggest that square-root minimizes the expected search size on
successful queries, claim that is supported by simulations \cite{LCCLS2002}.

In \cite{LCCLS2002}, a \emph{k-walker} query algorithm is presented and shown
that using it along side square-root allocation results in performance similar to
{\sl Gnutella}'s query flooding method but incurring up to two
orders of magnitude less network traffic. Also checks $3$ strategies for
replica placement, namely \emph{owner replication} where an object is replicated
at the requesting node, \emph{path replication} that caches the object along the
path from the requesting to the providing node and \emph{random replication}
where the replication is taking place randomly on visited nodes. Observations in
this work are not directly applicable to structured DHTs, because it is assumed
that the lookup time for an object depends only on the number of replicas and
not the placement strategy \cite{RS2004}.

The table below outlines how the $3$ allocation approaches fare:
%%
\begin{center}
{\footnotesize
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Uniform Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% When item is created, replicate its key in a fixed number of hosts.
low &
%
medium \\
\emph{Proportional Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% for each query, replicate the key in a fixed number of hosts (need to know or
% estimate the query rate)
medium &
%
low \\
\emph{Square Root Replication Allocation} &
% All (strictly) in-between strategies are (strictly) better than Uniform and
% Proportional - replication theory
medium &
% Assuming that each query keeps track of the search size then each time a query
% is finished the object is copied to a number of sites proportional to the
% number of probes that the search required.
medium &
% e.g. path replication is easy to scale, just detect the path along which the
% query ultimately got fulfilled
medium \\
\end{tabular}
}
\end{center}

{\sl Narada}~\cite{CRZ2000,CRSZ2001,CRSZ2002} is a generic
protocol for creating self-adapting overlay networks capable of 
application-layer multicast communications without requiring IP multicast
infrastructure at the network layer.
Although IP--multicast would present a choice in implementing
{\sl Narada}, it is in general considered that it violates the 
stateless design of the current Internet.
Despite the fact the {\sl Narada} was not designed as \p\ system per se,
it was the first (along with \emph{Scattercast} \cite{C2000}) to consider the
feasibility of overlay-based, application-layer services over the Internet while
taking into account bandwidth and latency properties of the underlying physical
infrastructure. In the context of this work, the inefficiency caused by the
topology mismatch and attempted to be tackled by building an highly connected
graph termed \emph{mesh}
with each source featuring its own minimum spanning tree. A gossip-protocol was
deployed for the creation of these spanning trees~\cite{LYL2008}.
%as shown in Figure~\ref{figure:narada}.
Both graph and trees are dynamically updated as nodes keep joining 
or departing the network. The protocol aims to ease the physical link stress,
the overall resource usage as well as the relative delay among end-systems. 
Unfortunately, the main limitation for {\sl Narada} is that 
although it works reasonably well for small groups, 
it does not scale well for larger networks. 
Hence, it is not a suitable choice for potentially large \p\ networks:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
medium &
% The overhead of Narada is proportional to the multicast group size
high &
% Maintaining the mesh for large multicast groups is expensive.
low
\end{tabular}
}
\end{center}

Along with {\sl Narada}, the \emph{Adaptive Overlay Topology 
Optimization (AOTO)} \cite{LZXN2003} is one of the first attempts to address the
topology mismatch problem. \emph{AOTO} is a distributed algorithm that seeks to
optimize the usage of the underlying physical resources and operates in
$2$ phases:
\emph{Selective Flooding} and \emph{Active Topology}.
In \emph{Selective Flooding}, a minimum spanning tree is built for each peer and
its immediate neighbors so that queries do not flood the entire network and at
the same time preventing their search scope from shrinking. This way some
neighbors become non--flooding. During \emph{Active Topology}, each peer
replaces independently such non--flooding neighbors, with closer nodes as an attempt
to revise the overlay links so that they can reflect more closely the physical
network topology. Picking a replacement out of these non-flooding
neighbors follows a random policy called \emph{Randomized AT} algorithm.
To accomplish the above actions, a peer has to keep track of 
its communication costs with all its neighbors (e.g., network delays)
as well as the costs between any pair of neighbors. The \emph{randomized AT}
algorithm is applied by a source peer
every time its neighbor list is updated or an updated neighbor cost 
table is received.
%%
%\paragraph*{Selective Flooding (SF)}
%
% TODO: I DON'T REMEMBER WHY THE FOLLOWING IS MENTIONING LTM WHICH IS ANOTHER
%       ALGORITHM. MAYBE THIS CAN BE USED AS A PART OF DISCUSSION AND/OR
%       COMPARISON OF AOTO AND LTM
% TODO: EDIT: LTM SEEMS A MISTAKE HERE BETTER NOT USE IT FOR DISCUSSION (THIS
%             IS AOTO)
%LTM's SF effectiveness has be proven to be detached from the different physical
% or overlay topologies. On the other hand, SF is more effective with large
%number of logical neighbors. It can reach an average optimization rate of 87.4
%percent on a logical topology with an average of 30 logical neighbors.
%
%\paragraph*{Active Topology (AT)}
%
%Different numbers of average logical neighbors has little to do with the
% effectiveness of AT. If the source has $n$ non-flooding peers, there are $n$
%potential neighbor replacements. The overhead to exhaust all $n$ possible
%replacements can be high, so in practice, after each replacement the source
%peer can decide whether it needs to find another candidate peer. This is done
%by computing the cost improvement ratio greater than some predefined
%termination threshold. The larger the threshold, the slower, in the number of
%optimization steps, the reduction of the normalized average distance. As a
%whole the average response time is significantly reduced when more optimization
%steps taken.
%%
\emph{AOTO}'s performance regarding the $3$ criteria is as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
medium &
% tracking of communication costs to all peer's neighbors as well as between
% any pair of neighbors. Whenever a new neighbor cost table is received or
% there is a change of neighbors, the source peer has to re-calculate the
% multicast tree and apply the randomized AT algorithm.
high &
% needs global knowledge
medium
\end{tabular}
}
\end{center}

@@

%$2knc_n^2c_e$. Simulation shows the best value for $k$ is $2$ or $3$. So, the

@@

\emph{LTM} fares as follows regarding our $3$  criteria:

@@

@@

As discussed above, \emph{THANCS} is fully distributed and needs only minimum knowledge
of, at most, a $2$-hop distant peers. This features renders 
the method a good candidate for large overlay networks. 
Also its topology adaptation helps construct a well fit overlay
with respect to the underlying network--at least with respect to network
distances. In addition, will-cut list and distance caches (which store already
probed peers) minimize the unnecessary messages for the network maintenance.
%%
In \cite{HLY2010}, the simulation-derived results of \emph{THANCS} as far
average broadcast delay and overlay improvement guarantees are discussed;
overall, \emph{THANCS} fares as follows regarding the $3$ stated criteria:

@@

For a incoming peer $Q$, 

@@

some group $A$’s neighbor groups is the same as the distance
between group $A$ and group $A$’s neighbor groups, then host $Q$

@@

In terms of the stated $3$ criteria, \emph{mOverlay} fares as follows:

@@

Protocols based on topology adaptation 
modify the topology of the \p\ network
using various schemes. The two most commonly used
create \emph{spanning tree}s using connection graphs
as well as  \emph{clusters} of physically close nodes.

@@

In landmark-based algorithms, nodes use network delay (e.g., \emph{RTT}) as a
distance measurement method to position themselves with respect to ``a priori''
known servers on the Internet, like \emph{Ono} which uses the \emph{CDN}-infrastructure
for this purpose.
For example, in Figure~\ref{figure:landmarking}, the newly
arriving peer, measures its distance to an array of landmark points denoted as
$L_n$. Then it creates an ordered list of the landmarks based on its measured
distances uses that information to select its neighbors. Specifically,
the landmark--servers are used by nodes to estimate 
their positions based on the intuitive assumption that peers
with similar distances to a set of landmarks, are physically close to each
other, as well, over the network.  
%%
\begin{figure}[ht]
\centering
  \includegraphics[scale=0.34]{img/pdf/landmarking.pdf}
\caption{Landmark binning during node bootstrap.}
\label{figure:landmarking}
\end{figure}

\input{unstructured-table}
\input{unstructured-plot}

>>>>

The \emph{directed BFS}
tries to avoid the aforementioned delay by forwarding 
query messages only to a selected subset of available neighbors. The selection
criteria varies, from the number of results received or the distance (hops)
traveled to locate these results, to the bandwidth, or the
query load of the neighbor. That way, fewer nodes are visited but quality of
query responses is maintained, to a large degree, on the premise that the
selected heuristics can direct the search to the right path.
%
In \emph{local indices},
each node indexes data hosted by neighboring nodes within a radius of $r$ hops
and uses this local index to answer queries on behalf of other nodes.
That way, local indices,
greatly reduce the aggregate bandwidth usage of the network and 
improve query efficiency. However, updating such indices in 
the presence of frequent node joins/departures 
may introduce significant overhead should the radius is kept broad.
%%
Below, we outline how the techniques in~\cite{YG-M2002}
fare against the three major performance criteria 
of Section~\ref{section:background}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \paragraph*{ \bf Delay Aware P2P System}
A \emph{delay--aware} \p\ system termed {\sl DAPS} 
was introduced in~\cite{ZL2005}.
{\sl DAPS}  seeks to attain reduced look-up times by dividing 
peer routing tables into several sectors of increasing delay. 
The source node that issues the query designates the delay 
boundary it may tolerate, providing so a \emph{pruning factor}.
In this context, user requests are forwarded only to 
nodes whose expected delay is less than or equal to the indicated boundary. 
{\sl DAPS} primarily focuses on user ``experience'' and deploys an
end-to-end delay monitoring mechanism that may enable
the clustering of routing tables. 
In a dynamic environment, the formation 
of very accurate such routing tables might be however an elusive goal.
%With the clustered
%routing tables and the loose organization of DAPS' overlay network it is
%considered by is be tween structured and unstructured.
%%
In terms of the three performance criteria, {\sl DAPS} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Does not check for close by nodes, it just sorts the contents of a node's
% routing table.
% Also in a high churn environment a lot of time could be spend probing for
% distances, resorting routing tables and creating sectors. Moreover it just
% prunes distant neighbor
low &
% Sorting routing table entries is done locally so it is not affecting.
low &
%
medium
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Gia}
The key objective of the {\sl Gia} system~\cite{CRBLS2003} is 
to help alleviate the scalability omnipresent
in unstructured \p\ file-sharing systems.
At first, {\sl Gia} replaced {\sl Gnutella}'s blind flooding 
with random walks.
Although this adoption was 
a step in the right direction \cite{LCCLS2002},
issuing a single copy of the query within the network
effectively reduces the search scope and may negatively affect 
the success rate of the query in question.
To overcome this limitation, {\sl Gia} introduces
a token-based flow control mechanism 
that gradually redirects queries to nodes which are more
likely to answer. This flow control mechanism also helps prevent node
overloading as each peer ``announces'' the number of query requests it 
can handle, in terms of tokens, to its neighbors; to this end, 
peers only forward query requests to nodes that they previously
received tokens from. Further refinement to the search mechanism is the
support for \emph{one--hop replication} of pointers to content.
{\sl Gia} also acknowledges the heterogeneity in peer bandwidth,
processing power, disk speed, etc., of \p\ nodes and uses this
information when connecting nodes to each other.
By using a topology adaptation algorithm, 
{\sl Gia} places low capacity nodes within 
short proximity to peers with high performance features.
This topology adaptation algorithm is based on the metric 
each node maintains about its satisfaction --ranging between $0$ and $1$--
for the neighbors it finds itself associated with. 
Through message exchange, a peer can establish new connections 
or drop superseded ones in order to improve its satisfaction.
Despite the fact that {\sl Gia}'s topology adaptation algorithm 
that primarily focuses on the satisfaction of peers improves the network's
scalability, it falls short in addressing the mismatch problem
as considerations for the underlying network are not handled in explicit
terms \cite{LXLNZ2005}. Moreover it reduces the search scope, exhibits poor
performance in the worst case when matching data is not found quickly
\cite{PR2004,HJ2004} and can potentially build  disconnected topologies
\cite{MBL2006}.
%
In terms of the three stated criteria, {\sl Gia}'s approach is as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Reduces the search scope.
medium &
% Only one copy of the query is issued to the network.
% A token based flow control mechanism redirects queries to nodes that are most
% likely to fulfill them.
low &
% Even thought the low overhead scalability is reduced by the reducing of
% search scope.
medium
\end{tabular}
}
\end{center}

@@

%$2knc_n^2c_e$. Simulation shows the best value for $k$ is $2$ or $3$ So, the

@@

\emph{LTM} fares as follows regarding our three  criteria:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Distributed Cycle Minimization Protocol (DCMP)}
Another problem with topology unaware
systems is the duplication of messages due to cycles in the network graph.
Interestingly, such cycles appear even along the correct forwarding path.
\cite{ZKB2008} focuses on this exact deficiency of overlay networks and
introduces the \emph{Distributed Cycle Minimization Protocol
(DCMP)}, a dynamic, fully distributed method that removes cycles;
this is accomplished without sacrificing
overlay connectivity, resilience and other key properties of unstructured
\p\ architectures and by avoiding a hierarchical organization of peers. 
Once a cycle is detected in {\it DCMP}, the most powerful node in that cycle 
is elected as the \emph{Gate Peer} and the cycle is then broken in that place
that it will result in the minimization of the distance between the
\emph{Gate Peer} and all other nodes that are currently part of the cycle. 
This process is managed by using two specialized message types 
namely, \emph{Information Collection Message (ICM)} and \emph{Cut Message (CM)}. 
\emph{DCMP} bases its operation on messages whose travel is limited by an
imposed \emph{TTL} value (max set to $7$ for most cases). This inherently limits
the protocol in detecting cycles that span for more than \emph{TTL} nodes.
Even though cycle elimination does improve network performance, 
it cannot  directly contribute to the solution of the topology mismatch
problem, while its performance in a high traffic and churn environments and its
ability to retain important characteristics of a {\sl Gnutella}-like topology (i.e.,
like degree distribution, average peer distance, diameter e.t.c.) has been
doubted~\cite{CSG2010}. 
On the other hand, even though some of the overhead
saved by the duplicate message reduction is spent to control the cycle cutting
mechanism, it is reported that it does a lot better in that area
due to its ``lazy'' broadcasting of control messages, as opposed to, for example,
LTM's periodic approach \cite{ZKB2008}.
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/dcmp.jpeg}
%\caption{Cycle elimination methods in DCMP}
%\label{figure:dcmp}
%\end{figure}
%
% TODO: SOME DISCUSSION
%Actually, the duplicate packet problem seems to hurt more the active nodes;
%those with higher capacities and bandwidth that contribute the most to the
%network.
The expected \emph{DCMP} behavior as far as our three criteria is:
%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It returns more result than LTM according to experiments in
% \cite{ZKB2008}
medium &
% Duplicates are an important fraction of the redundant overhead imposed by
% topology mismatch and thus DCMP minimizes this as possible.
% It is reported though that still stays for example one to two orders of
% magnitude less than LTM due to its ``lazy'' broadcasting of control messages
% (as opposed to LTM's periodic approach) \cite{ZKB2008}.
low &
% fully distributed method
high
\end{tabular}
}
\end{center}

In \cite{CS2002} and \cite{LCCLS2002}, replication is used as a way to improve
inefficient blind search. The observation is that as the number of replicas
increases in the network, it would be relatively easy to locate items even if
search is random. Concretely, three three approaches for replication allocation
are discussed: \emph{uniform}, \emph{proportional}, and
\emph{square-root replication}.

In the uniform model, all objects are replicated without taking into account
the query distribution,
while in the proportional, objects are replicated analogously to their query
rate, so that frequently queried items can be found more often. Experimental
outcomes indicate that the uniform allocation minimizes the maximum search
length and so it can reduce the time spent on unsuccessful searches. The
proportional strategy effectively decreases the search time for popular items,
but suffers when needing to locate the rare entities. When it comes to expected
successful search size, it is the same for for both uniform and proportional
models and any approach in between to always behave much better. Finally, the
square-root model is an attempt to find the golden ratio between uniform and
proportional allocation models. It suggests setting the number of object
replicas to the square root of the searching rate for an object\footnote{An
interesting application of the square-root principle has also been explored
in the context of topology reconstruction, by ensuring node degree to be
proportional to the square-root of its content popularity \cite{C2005}.}.
Theory in \cite{CS2002} suggest that square-root minimizes the expected search size on
successful queries, claim that is supported by simulations \cite{LCCLS2002}.

In \cite{LCCLS2002}, a \emph{k-walker} query algorithm is presented and shown
that using it along side square-root allocation results in performance similar to
{\sl Gnutella}'s query flooding method but incurring up to two
orders of magnitude less network traffic. Also checks three strategies for
replica placement, namely \emph{owner replication} where an object is replicated
at the requesting node, \emph{path replication} that caches the object along the
path from the requesting to the providing node and \emph{random replication}
where the replication is taking place randomly on visited nodes. Observations in
this work are not directly applicable to structured DHTs, because it is assumed
that the lookup time for an object depends only on the number of replicas and
not the placement strategy \cite{RS2004}.

The table below outlines how the three allocation approaches fare:
%%
\begin{center}
{\footnotesize
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Uniform Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% When item is created, replicate its key in a fixed number of hosts.
low &
%
medium \\
\emph{Proportional Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% for each query, replicate the key in a fixed number of hosts (need to know or
% estimate the query rate)
medium &
%
low \\
\emph{Square Root Replication Allocation} &
% All (strictly) in-between strategies are (strictly) better than Uniform and
% Proportional - replication theory
medium &
% Assuming that each query keeps track of the search size then each time a query
% is finished the object is copied to a number of sites proportional to the
% number of probes that the search required.
medium &
% e.g. path replication is easy to scale, just detect the path along which the
% query ultimately got fulfilled
medium \\
\end{tabular}
}
\end{center}

{\sl Narada}~\cite{CRZ2000,CRSZ2001,CRSZ2002} is a generic
protocol for creating self-adapting overlay networks capable of 
application-layer multicast communications without requiring IP multicast
infrastructure at the network layer.
Although IP--multicast would present a choice in implementing
{\sl Narada}, it is in general considered that it violates the 
stateless design of the current Internet.
Despite the fact the {\sl Narada} was not designed as \p\ system per se,
it was the first (along with \emph{Scattercast} \cite{C2000}) to consider the
feasibility of overlay-based, application-layer services over the Internet while
taking into account bandwidth and latency properties of the underlying physical
infrastructure. In the context of this work, the inefficiency caused by the
topology mismatch is attempted to be tackled by building a highly connected
graph, termed \emph{mesh},
with each source featuring its own minimum spanning tree. A gossip-protocol was
deployed for the creation of these spanning trees~\cite{LYL2008}.
%as shown in Figure~\ref{figure:narada}.
The graph and trees are dynamically updated as nodes keep joining 
or departing the network. The protocol aims to ease the physical link stress,
the overall resource usage as well as the relative delay among end-systems. 
Unfortunately, the main limitation for {\sl Narada} is that 
although it works reasonably well for small groups, 
it does not scale well for larger networks. 
Hence, it is not a suitable choice for potentially large \p\ networks:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
medium &
% The overhead of Narada is proportional to the multicast group size
high &
% Maintaining the mesh for large multicast groups is expensive.
low
\end{tabular}
}
\end{center}

Along with {\sl Narada}, the \emph{Adaptive Overlay Topology 
Optimization (AOTO)} \cite{LZXN2003} is one of the first attempts to address the
topology mismatch problem. \emph{AOTO} is a distributed algorithm that seeks to
optimize the usage of the underlying physical resources and operates in
$2$ phases:
\emph{Selective Flooding} and \emph{Active Topology}.
In \emph{Selective Flooding}, a minimum spanning tree is built for each peer and
its immediate neighbors so that queries do not flood the entire network and at
the same time preventing their search scope from shrinking. This way some
neighbors become non--flooding. During \emph{Active Topology}, each peer
replaces independently such non--flooding neighbors, with closer nodes as an attempt
to revise the overlay links so that they can reflect more closely the physical
network topology. Picking a replacement out of these non-flooding
neighbors follows a random policy called \emph{Randomized AT} algorithm.
To accomplish the above actions, a peer has to keep track of 
its communication costs with all its neighbors (e.g., network delays)
as well as the costs between any pair of neighbors. The \emph{randomized AT}
algorithm is applied by a source peer
every time its neighbor list is updated or an updated neighbor cost 
table is received.
%%
%\paragraph*{Selective Flooding (SF)}
%
% TODO: I DON'T REMEMBER WHY THE FOLLOWING IS MENTIONING LTM WHICH IS ANOTHER
%       ALGORITHM. MAYBE THIS CAN BE USED AS A PART OF DISCUSSION AND/OR
%       COMPARISON OF AOTO AND LTM
% TODO: EDIT: LTM SEEMS A MISTAKE HERE BETTER NOT USE IT FOR DISCUSSION (THIS
%             IS AOTO)
%LTM's SF effectiveness has be proven to be detached from the different physical
% or overlay topologies. On the other hand, SF is more effective with large
%number of logical neighbors. It can reach an average optimization rate of 87.4
%percent on a logical topology with an average of 30 logical neighbors.
%
%\paragraph*{Active Topology (AT)}
%
%Different numbers of average logical neighbors has little to do with the
% effectiveness of AT. If the source has $n$ non-flooding peers, there are $n$
%potential neighbor replacements. The overhead to exhaust all $n$ possible
%replacements can be high, so in practice, after each replacement the source
%peer can decide whether it needs to find another candidate peer. This is done
%by computing the cost improvement ratio greater than some predefined
%termination threshold. The larger the threshold, the slower, in the number of
%optimization steps, the reduction of the normalized average distance. As a
%whole the average response time is significantly reduced when more optimization
%steps taken.
%%
\emph{AOTO}'s performance regarding the three criteria is as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
medium &
% tracking of communication costs to all peer's neighbors as well as between
% any pair of neighbors. Whenever a new neighbor cost table is received or
% there is a change of neighbors, the source peer has to re-calculate the
% multicast tree and apply the randomized AT algorithm.
high &
% needs global knowledge
medium
\end{tabular}
}
\end{center}

@@

As discussed above, \emph{THANCS} is fully distributed and needs only minimum knowledge
of, at most, a $2$-hop distant peers. This features renders 
the method a good candidate for large overlay networks.
Also its topology adaptation helps construct a well fit overlay
with respect to the underlying network--at least with respect to network
distances. In addition, will-cut list and distance caches (which store already
probed peers) minimize the unnecessary messages for the network maintenance.
%%
\emph{THANCS} reportedly improves brodcast performance the extent of which, though,
depends on the underlying network since \emph{THANCS} does not provide the
performance guarantee for the improvement of any given overlay topology~\cite{HLY2010}.

@@

For an incoming peer $Q$, 

@@

some group $A$'s neighbor groups is the same as the distance
between group $A$ and group $A$'s neighbor groups, then host $Q$

@@

In terms of the stated three criteria, \emph{mOverlay} fares as follows:

@@

Protocols based on topology adaptation 
modify the topology of the \p\ network
using various schemes, the two most common of which
create either \emph{spanning tree}s using connection graphs
or \emph{clusters} of physically close nodes.

@@

In landmark-based algorithms, nodes use network delay (e.g., \emph{RTT}) as a
distance measurement method to position themselves with respect to ``a priori''
known servers on the Internet, like \emph{Ono} which uses the \emph{CDN}-infrastructure
for this purpose.

\begin{figure}[ht]
\centering
  \includegraphics[scale=0.34]{img/pdf/landmarking.pdf}
\caption{Landmark binning during node bootstrap.}
\label{figure:landmarking}
\end{figure}

\input{unstructured-table}
\input{unstructured-plot}
%%
For example, in Figure~\ref{figure:landmarking}, the newly
arriving peer, measures its distance to an array of landmark points denoted as
$L_n$. Then it creates an ordered list of the landmarks based on its measured
distances uses that information to select its neighbors. Specifically,
the landmark--servers are used by nodes to estimate 
their positions based on the intuitive assumption that peers
with similar distances to a set of landmarks, are physically close to each
other, as well, over the network.
